Finding Quality Issues in SKOS Vocabularies

### 2012-03-28 introduction.tex
updated background (and intro)

On the other hand, existing guidelines consider these aspects, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger vocabularies \todo{AI}{Refer to Spero's example if there is space}. The SKOS context, in which vocabularies can be linked on the Web to other resources, also brings new issues, hitherto unforeseen by ``traditional'' quality checking approaches.

@@

We aim at contributing to the ongoing efforts of the community to bridge that gap\todo{Bernhard, Christian}{I'm not so happy with my sentence here. We can remove it if there's no better alternative to send the message we can remove it!}. Our goal is to help taxonomists in identifying possible quality issues in SKOS vocabularies, which go beyond data model integrity conditions while still applying to a wide range of cases. We want to give them a set of computable quality checking functions that, in combination with the taxonomists' experience and domain expertise, can serve as quality indicators for vocabularies. Finding such quality issues also gives important feedback on the overall vocabulary design process and should, at the end, lead to better vocabularies. The main contributions of this work can be summarized as follows:

>>>>

On the other hand, existing guidelines consider these aspects, but currently rely on \textbf{human judgement}, which is subjective and does not scale for larger vocabularies. The SKOS context, where vocabularies can be linked together on the Web, also brings issues hitherto unforeseen by traditional checking approaches.

@@

We aim to contribute to the ongoing efforts of the community to bridge that gap\todo{BH, CM}{I'm not so happy with my sentence here. We can remove it if there's no better alternative to send the message we can remove it!}. Our goal is to help taxonomists in identifying possible quality issues in SKOS vocabularies, which go beyond data model integrity conditions while still applying to a wide range of cases. We want to give them a set of computable quality checking functions that, in combination with the taxonomists' experience and domain expertise, can serve as quality indicators for vocabularies. Finding such quality issues also gives important feedback on the overall vocabulary design process and should, at the end, lead to better vocabularies. The main contributions of this work can be summarized as follows:
